% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage[utf8]{inputenc}
\usepackage{polski}

\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 

\name{ANNA WARPECHOWSKA\\[12pt]}     % the \\[12pt] adds a blank
				        % line after name      

\begin{resume}
%\address{\bf PRESENT ADDRESS\\193 5th Avenue\\Troy, NY 12180\\(518) 274-1234}
\section{PERMANENT ADDRESS}
Piórkowska 10a\\17-132 Wyszki\\Poland\\692-819-605
%\address{\bf PERMANENT ADDRESS\\Piórkowska 10a\\19-500 Wyszki\\Poland}
%\address{\bf PERMANENT ADDRESS \\ 110 Brant Avenue \\  Upper Saddle
%         River,   NJ 07458 \\  (201) 555-9509}
                                  

%\section{JOB OBJECTIVE}          
%    A summer position that will use my accounting and computer
%    skills.          
 
\section{EDUCATION (COMPLETED)}
	Białystok University of Technology, \\
	Bachelor of Science, Computer Science, September 2008 -- February 2012 \\
	Thesis: IT System aiding the process of validating SQL queries.

\section{EDUCATION (IN PROGRESS)}
	Białystok University of Technology, \\
	Master of Science, Computer Science, March 2012-Present \\
	Concentration in Software Engineering \\
	Thesis: Multi-class Support Vector Machines. \textit{(in progress)}

\section{EDUCATION (ON HOLD)}
	Białystok University of Technology, \\
	Bachelor of Science, Mathematics, September 2009-June 2012 \\
	Finished the 3 year university course without completing the final thesis.
	% Thesis: TEMAT. \textit{(on hold)}
   % Rensselaer Polytechnic Institute, Troy, NY  \\        
   % Bachelor of Science, Management, May 1990   \\       
   % Concentration in Management Systems       \\   
   % Minors in Computer Science and Economics  \\        
   % G.P.A. 3.3/4.0          
\section{EXPERIENCE}
   \vspace{-0.1in}	

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Programmer - Internship} \>DevCore(\textit{www.devcore.pl}) \>July 2011\\
                             \>Białystok, Poland
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Internship involved the development of web applications in APS.NET framework.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Programmer - Internship} \>Sygnity(\textit{www.sygnity.pl}) \>November 2011\\
                             \>Białystok, Poland
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Internship involved the development and maintenance of IT systems using Oracle SQL software.

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Software Developer} \>Sygnity(\textit{www.sygnity.pl}) \>December 2011 -- present\\
                             \>Białystok, Poland
   \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   Sygnity is one of the largest IT companies in Poland, providing solutions to both commercial customers and public institutions.
   Sygnity has been operating in the Polish market for 20 years, and currently employs over 1,500 people.
   I have been working as a Software Developer specialising in the Oracle SQL systems. My responsibilities are both maintenance as well as
   the development of the new IT systems.
   During that time I participated in the development of 2 new projects, while maintaining several existing ones.

   %\begin{tabbing}
   %\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   % {\bf Programmer - Internship} \>EO Networks SA (\textit{www.eo.pl}) \>July 2011\\
   %                          \>Białystok, Poland
   %\end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
   % Internship involved developing web application in JSP/Liferay in a small team.
   %\begin{tabbing}
   %\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   % {\bf Programmer} \>CodiLime \textit{(www.codilime.com)} \> April 2012 - August 2012\\
   %                       \>Białystok, Poland
   %\end{tabbing}\vspace{-20pt}
   % Developing security layer for an existing credit card transaction system.

\section{PROGRAMMING AND DEVELOPMENT SKILLS}
	Proficient development skills:
	\begin{itemize}
		\item Oracle PL/SQL
		\item Oracle Forms
		\item Oracle Reports
		\item Enterprise Architect
	\end{itemize}

	Good development skills:
	\begin{itemize}
		\item Python (Django framework)
		\item Perl
		\item C++
		\item MATLAB
	\end{itemize}
	Good knowledge of Windows and Linux operating system, database systems (Oracle, MySQL) and revision control systems (SVN, GIT)\\
	Good mathematical, algorithmic and problem solving skills.\\
	Other: Good knowledge of \LaTeX \\
 
%\section{HONORS AND AWARDS}
%	Third place in region in Polish nationwide mathematics competition ``Kwadratura Koła''. Middle school, Spring 2004.\\
%	Finalist of the XII All-Poland English Olympics for Technical Universities, Poznań 2011.\\
%	Laureate (Third place) of the XIII All-Poland English Olympics for Technical Universities, Poznań 2012.\\
%	Completed Google Summer of Code program May-August 2012.\\
%	First place in II contest of Foreign Language Centre and Dean of Faculty of Computer Science in English, \emph{May 2012}\\
%	Third place in XI regional team programming competition ``XI Podlaski Turniej w Programowaniu Zespołowym'', 24-25 November 2012.\\
%	Member of ``Pogromcy Algorytmów'' - students scientific group section dedicated to algorithms and data structures, 2008-2013.\\

\section{CERTIFICATES AND LICENSES}
	Passed the examination in English at CEFR level: B1. \\
	Driver's Licence. \\

\section{EXTRACURRICULAR ACTIVITIES}          
	Recreational Mathematics. \\
	Music. \\
 
\end{resume}
\end{document}
